Miscellaneous notes for D. Huybrechts's Complex Geometry

### 2016-09-18 Complex Geometry - index/misc/complex geometry-misc.tex
Solved one problem in "complex geometry". Start to learn the code for green functions.

\maketitle
\abstract{
Miscellaneous notes for D. Huybrechts's book \textit{Introduction
to Complex Geometry}, include some homeworks done.
}
\tableofcontents
\section{The structure of almost complex structures on \texorpdfstring{$\mathbb{R}^{2n}$}{}}
\label{sec:The_structure_of_almost_complex_structures_on_R2n}
In exercise 1.2.1, it says that the set of all compatible almost complex
structures on a euclidean space of dimension $2n$, is two copies of $S^2$.

@@

Then I discover this too hard to work, because too many equations are
involed, and none of them could be eliminiated by other. Meanwhile, I
found a post in Math.SE about this \cite{math.se_1}.

@@

    \marginpar{Here I digressed to another problem. I will come back later.}
    To understand that post, I read this\cite{math.se_2}. However, the answer
    in the second post is not perfect:

@@

    This proof is not complete because, to build the proof from 
    $\mathbb{R}^2$ to $\mathbb{R}^{2n}$, it requries, in his argument, that
    any element in $\mathrm{GL}(V\oplus V)$ is in the image of
    $\mathrm{GL}(V)\times \mathrm{GL}(V')$, which is not the case.

@@

@@

        The proof is quite straightforward and is omitted.
        \subsubsection{Why \texorpdfstring{$M_n = \frac{GL(2n,\mathbb{R})}
            {GL(n,\mathbb{C})}$}{} (continued)}

        Coming back to my point. This is a note of my question on
        Math.SE\cite{math.se_3}

        I questioned him:
        \begin{enumerate}
            \item Why $AJA^{-1}$ is the same almost-complex structure 
                $J$ if and only if $A\in \mathrm{GL}(n;\mathbb{C})$. 
            \item Why all almost-complex structures are similar over 
                $\mathbb{R}$.
        \end{enumerate}
        He responsed that:
        \begin{enumerate}
            \item is the definition of $\mathrm{GL}(n;\mathbb{C})$
                as matrices $A$ with $AJA^{-1}=J$.
            \item comes from the fact that any real matrices that are 
                similar over $\mathbb{C}$ are already similar over 
                $\mathbb{R}$. This isn't trivial but it has been asked 
                and answered many times on this site: here is one 
                reference \url{http://math.stackexchange.com/questions/57242/similar-matrices-and-field-extensions?noredirect=1&lq=1}
        \end{enumerate}

        Inside the reference, the following theorem is proved:

        \begin{thm}
            Let $E$ be a field, let $F$ be a subfield, and let $A$ and
            $B$ be $nxn$ matrices with coefficients in $F$. If $A$ and
            $B$ are similar over $E$, they are similar over $F$.
        \end{thm}
% TODO also, this post may be useful:http://math.stackexchange.com/questions/1400917/equivalence-of-almost-complex-structures

\section{Anchor}
\label{sec:Anchor}

\begin{thebibliography}{1}
  \bibitem{book} D Huybrechts's Introduction to Complex Geometry.
  \bibitem{math.se_1} \href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}.
  \bibitem{math.se_2} \href{http://math.stackexchange.com/questions/1356823/does-gln-mathbbc-inject-into-gl2n-mathbbr-for-all-n}{Does $GL(n,\mathbb{C})$ inject into $GL^+(2n, \mathbb{R})$ for all $n$?}
  \bibitem{determinants_of_block_m} John R. Silvester, 
      Determinants of Block Matrices. Available in WebArchive link:
      \url{https://web.archive.org/web/20140505161153/http://www.mth.kcl.ac.uk/~jrs/gazette/blocks.pdf}
  \bibitem{math.se_3} \href{http://math.stackexchange.com/questions/1927487/making-sense-of-frac-mathrmgl2n-mathbbr-mathrmgln-mathbbc/1927518?noredirect=1#comment3957369_1927518}{Making sense of $\frac{\mathrm{GL}(2n,\mathbb{R})}{\mathrm{GL}(n,\mathbb{C})}$}
\end{thebibliography}
\printnomenclature

>>>>

\maketitle
\abstract{
Miscellaneous notes for D. Huybrechts's book \textit{Introduction
to Complex Geometry}, include some homeworks done.
}
\tableofcontents
\section{The structure of almost complex structures on \texorpdfstring{$\mathbb{R}^{4}$}{}
  (exercise 1.2.1)}
\label{sec:The_structure_of_almost_complex_structures_on_R2n}
In exercise 1.2.1, it says that the set of all compatible almost complex
structures on a euclidean space of dimension $2n$, is two copies of $S^2$.

@@

Then I discover this too hard to work, because too many equations are
involed, and none of them could be eliminiated by other. Meanwhile, I
found a post in Math.SE about this \cite{math.se_1}. Here are several
important concepts for understanding that post.

@@

        \subsubsection{Why \texorpdfstring{$M_n = \frac{GL(2n,\mathbb{R})}
            {GL(n,\mathbb{C})}$}{}}

        This is a note of my question on Math.SE\cite{math.se_3}, which
        explains that we can identify the set of almost complex structures
        with $\frac{GL(2n,\mathbb{R})}{GL(n,\mathbb{C})}$.

        I questioned him:
        \begin{enumerate}
            \item Why $AJA^{-1}$ is the same almost-complex structure 
                $J$ if and only if $A\in \mathrm{GL}(n;\mathbb{C})$. 
            \item Why all almost-complex structures are similar over 
                $\mathbb{R}$.
        \end{enumerate}
        He responsed that:
        \begin{enumerate}
            \item is the definition of $\mathrm{GL}(n;\mathbb{C})$
                as matrices $A$ with $AJA^{-1}=J$.
            \item comes from the fact that any real matrices that are 
                similar over $\mathbb{C}$ are already similar over 
                $\mathbb{R}$. This isn't trivial but it has been asked 
                and answered many times on this site: here is one 
                reference \cite{math.se_4}.
        \end{enumerate}

        Inside that reference, the following theorem is proved:

        \begin{thm}
            Let $E$ be a field, let $F$ be a subfield, and let $A$ and
            $B$ be $nxn$ matrices with coefficients in $F$. If $A$ and
            $B$ are similar over $E$, they are similar over $F$.
        \end{thm}

        However, I still have doubts about the following question:
        For $A\in \mathrm{GL}(2n,\mathbb{R})$, if $AJA^{-1}=J$, can we
        conlude that $A$ is inside $\mathrm{GL}(n,\mathbb{C})$?
        % TODO resolve this double.
        \subsubsection{Why \texorpdfstring{
                $GL(n, \mathbb{C}) \hookrightarrow GL^+(2n,\mathbb{R})$
                }{}
            }

        To understand that post \cite{math.se_1}, I also read this
        \cite{math.se_2}. In it, it asks how to prove that 
        \begin{align}
            \label{eq:sec.1.1.2_why_glnc_injectInto_positive_comp}
            GL(n, \mathbb{C}) \hookrightarrow GL^+(2n,\mathbb{R})
        \end{align}
        for any $n$. The questioner gives the intuition for this fact:
        \begin{quote}
            how about since as Lie groups, $GL(n,\mathbb{C}) 
            \subset GL(2n, \mathbb{R})$ and $GL(n,\mathbb{C})$ is connected 
            but $GL(2n, \mathbb{R})$ has two connected components, one for 
            positive determinant and one for negative determinant? And the 
            identity has positive determinant, so it must lie in that 
            component.
        \end{quote}

        Someone answered that question:

@@

        However, this proof is not complete because, to build the proof from 
        $\mathbb{R}^2$ to $\mathbb{R}^{2n}$, it requries, in his argument, that
        any element in $\mathrm{GL}(V\oplus V)$ is in the image of
        $\mathrm{GL}(V)\times \mathrm{GL}(V')$, which is not the case.

@@

% TODO also, this post may be useful:http://math.stackexchange.com/questions/1400917/equivalence-of-almost-complex-structures

@@

        The proof is quite straightforward and is omitted.

        \subsubsection{Why \texorpdfstring{
                $GL(n, \mathbb{C}) \hookrightarrow GL^+(2n,\mathbb{R})$
                }{}(continued)
            }
        With above theorem, the proof of equation 
        \ref{eq:sec.1.1.2_why_glnc_injectInto_positive_comp} 
        is straight forward. Since for 
        $(a_{ij})= A\in \mathrm{GL}(n,\mathbb{C})$, it injects into
        $\mathrm{GL}(2n,\mathbb{R})$ as matrices of the form:
        \begin{align*}
            \left( \begin{array}{ccc}
             \text{...} & \text{...} & \text{...} \\
             \text{...} & H a_{\text{ij}} & \text{...} \\
             \text{...} & \text{...} & \text{...} \\
            \end{array} \right)
        \end{align*}
        where:
        \begin{align*}
            H(z\equiv x+iy)=\left( \begin{array}{cc}
                    x & -y \\
                    y & x \\
            \end{array}\right)
        \end{align*}
        Since $H(a_{ij})$ commutes with each other (proved by calculation),
        we can use the theorem in previous part to show that:
        \begin{align*}
            \mathrm{det_\mathbb{R}}(A) =
            \mathrm{det_\mathbb{R}}  (\mathrm{det_\mathbb{C}}(A))
            = |\mathrm{det_\mathbb{C}}(A) |^2 \geq 0
        \end{align*}
        Notice that I have been sloopy in language, but the meaning should
        be clear.
\section{Anchor}
\label{sec:Anchor}

\begin{thebibliography}{1}
  \bibitem{book} D Huybrechts's Introduction to Complex Geometry.
  \bibitem{math.se_1} \href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}.
  \bibitem{math.se_2} \href{http://math.stackexchange.com/questions/1356823/does-gln-mathbbc-inject-into-gl2n-mathbbr-for-all-n}{Does $GL(n,\mathbb{C})$ inject into $GL^+(2n, \mathbb{R})$ for all $n$?}
  \bibitem{determinants_of_block_m} John R. Silvester, 
      Determinants of Block Matrices. Available in WebArchive link:
      \url{https://web.archive.org/web/20140505161153/http://www.mth.kcl.ac.uk/~jrs/gazette/blocks.pdf}
  \bibitem{math.se_3} \href{http://math.stackexchange.com/questions/1927487/making-sense-of-frac-mathrmgl2n-mathbbr-mathrmgln-mathbbc/1927518?noredirect=1#comment3957369_1927518}{Making sense of $\frac{\mathrm{GL}(2n,\mathbb{R})}{\mathrm{GL}(n,\mathbb{C})}$}
  \bibitem{math.se_4} \href{http://math.stackexchange.com/questions/57242/similar-matrices-and-field-extensions?noredirect=1&lq=1}
  {Similar matrices and field extensions}
\end{thebibliography}
\printnomenclature
